Well-being of Individuals from the United States Global Social Survey are Affected by Finances, Relationships, and Health

### 2023-03-16 outputs/paper/paper3.qmd
Updated quarto doc

quartoclean5 <- read_csv("../inputs/data/clean5.csv")

@@

# Introduction

# Data Source

# Data Gathering

# Results

```{r}
#| label: fig-satfincome
#| fig-cap: Visualization of...
#| echo: false

@@

# Discussion

# Appendix

>>>>

quartoclean5 <- read_csv("../../inputs/data/clean5.csv")

@@

# 1 Introduction

# 2 Data

## 2.1 Tools Used

## 2.2 Survey Methodology

## 2.3 Survey Biases and Ethics

## 2.4 Data Collection

## 2.5 Data Cleaning

# 3 Results

\newpage

```{r}
#| label: fig-satfincome
#| fig-cap: Visualization of financial satisfaction of respondents with respect to their relative income. There is a larger proportion of respondents that claim that they are not satisfied with their finances at lower income ranges. As the income range increases, more respondents proportionally express that they are either more of less satisfied, or are pretty well satisfied with their financial situation.
#| echo: false

@@

# 4 Discussion

## 4.1 Limitations

# 5 Appendix
